Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-08-11 paper/main.tex
revise structure of introduction

% brain mapping via fMRI
Cognitive neuroscientists use brain imaging methods like blood oxygenation
level-dependent functional magnetic resonance imaging (BOLD fMRI) to map
perceptual and cognitive brain processes (e.g. viewing of landscapes,
\citep{epstein1998ppa}; or theory of mind \citep{spunt2014validating}) to
functional brain areas or networks.
% simplified stimuli
Brain mapping studies have traditionally employed small sets of carefully
chosen, simplified stimuli to strictly control experimental conditions.
% disadvantage 1: validity
Their disadvantage is that a limited number of simplified stimuli does not
resemble our real-life experience and thus lack external validity
\citep{westfall2016fixing} as well as ecological validity
\citep{hasson2004intersubject}.
% disadvantage 2: averaging for group results
Additionally, brain mapping studies usually average results across at least
10-15 subjects to improve the signal-to-noise-ratio (SNR). The disadvantage here
is that the averaging approach does not characterize brain functions at an
individual level, a prerequisite for the application of brain imaging methods in
individual diagnostics (cf. \citep{dubois2016building, eickhoff2020towards}).

@@

% What is the PPA?
A classic example of a functional, higher-level visual area is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location
The PPA is located in the posterior parahippocampal gyrus at the boundary to the
anterior lingual gyrus and medial fusiform gyrus, both being part of the ventral
visual stream \citep{mishkin1982contribution, goodale1992separate}.
% neural correlate of scene perception
Increased hemodynamic activity in the PPA correlates with the perception of
static pictures of landscapes or landmarks compared to pictures of tools or
faces.
% spatial layout hypothesis
According to the spatial layout hypothesis, the PPA is involved in
processing the surface geometry of a visual stimulus and possibly in identifying
scenes based on their spatial layout \citep{epstein2010reliable}.

% literature review overview 1: imagination & haptic exploration
At a group average level, results generalize to mental imagination of landscapes
\citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO
blocks \citep{wolbers2011modality}.
% literature review overview 2: spoken sentences
One study that used spoken, place-related sentences showed significantly
decreased activation in the left and no modulation in the right-hemispheric PPA
\citep{aziz2008modulation}.

@@

% Wolbers: haptic exploration
In the block design study conducted by \citep{wolbers2011modality} the PPA of
sighted participants showed increased activation during a delayed
matching-to-sample task of haptically explored scenes constructed from LEGO
bricks compared to haptically explored abstract geometric objects.

\todo[inline]{Er hat noch eine Connectivitäts-Analyse mit dem Occipital Cortex
    gemacht. Im Vergleich zum visuellen Paradigma ist im haptischen Paradigma
    keine Connectivität. Interpretation: Es kann keine mental imagery sein;
    ``The scene-related increase in coupling with the PPA was significantly
    stronger in multiple clusters in occipital cortex under visual than haptic
    stimulation (Figure 2B; Table S2)''}

% Aziz (2008): place related sentences
\todo[inline]{Aziz hat auf eine zweite Mail geantwortet: Sie modelt die HRF über
den jeweils gesamten Satz von ca. 2.8 Sekunden}

\todo[inline]{lass uns kurz im Gespräch über Aziz Paper gucken; die relvanten
    Abschnitte sind in der PDF markiert. Ihre Method Section ist ``strange'' und
    im Grunde kommt überall nur uneinheitliche Grütze heraus; ich blicke nicht
    durch, weshalb folgendes nicht vollständig korrekt sein wird;so wie ich es
    verstanden habe, hat sie den Unterschied zwischen PPA und FFA angeguckt,
aber diesen Unterschied im Kontrast zu object-related Sentences (dortige Fig 3;
)}

% Aziz' stimuli
To our knowledge only one study by \citep{aziz2008modulation} correlated
hemodynamic activity of the PPA with spoken sentences. Sentences described
generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting
pool''), faces  (``Marilyn Monroe has a large square jaw''), or objects (``The
television has a long antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.

@@

% summary if literature review
In summary, studies suggest that the PPA does not exclusively respond to
visually presented spatial information. Nevertheless, the question how the
PPA responds to auditory stimuli is still open.

\todo[inline]{but Huth et al. (2016) implicitly; but they do not discuss the
PPA; moreover, they do voxel-wise encoding which doesn't say anything about
excitation/inhibition}

% shortcomings of previous studies: simplified stimuli
All reviewed studies used a small set of carefully designed, simplified stimuli
to strictly control experimental conditions.
% shortcomings of previous studies: task-based paradigm
They further relied on explicit judgment-based tasks to ensure that participants
payed attention to the stimuli.
% second question: life-like conditions
This raises the second question which is how the PPA behaves under life-like
conditions.
% naturalistic stimuli
Naturalistic stimuli like movies \citep{hasson2008neurocinematics,
sonkusare2019naturalistic} or narratives \citep{honey2012not,
lerner2011topographic, silbert2014coupled} offer complex, continuous stimuli
that better resemble our experience of a our dynamic environment.

% naturalistic stimuli review: intro
Two early studies using naturalistic stimuli suggest functional specialization
of brain areas is preserved during movie watching when many perceptual and
cognitive processes are triggered simultaneously \citep{bartels2004mapping, hasson2004intersubject}.
% Bartels (2004): Film + GLM (but surprisingly did not annotate landscapes)
\citep{bartels2004mapping} manually annotated time points that depict faces and
human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}
\citep{tomorrowneverdies}.
% Bartels: results
Employing a general linear model (GLM) to model hemodynamic activity, these time
points correlated with increased activity in the ``fusiform face area''
\citep{kanwisher1997ffa} and ``extrastriate body area''
\citep{downing2001bodyarea} respectively.
% Hasson (2004): Film + (reverse) ISC
Employing a reverse intersubject correlation, \citep{hasson2004intersubject}
used a 30 minute clip of the movie \textit{The Good, the Bad, and the Ugly}
\citep{goodbadugly}.
% Hasson: method
fMRI brain volumes showing the highest hemodynamic activity
in the PPA [across (five) participants] were matched to the temporally
corresponding movie frames.
% Hasson: results
Results revealed that corresponding movie frames
depicted indoor and outdoor scenes including buildings and open fields.

% summary naturalistic stimuli
Nevertheless, both studies used an audio-visual stimulus and thus do not address
the question how the PPA responds to spatial clues that are embedded in a
complex, audio-only stimulus.

\todo[inline]{mih: Possibly cite https://psyarxiv.com/sdbqv/ (DuPre (2019).
Nature abhors a paywall) and declare that this study is a concrete realization
of that promise}

% what we did: data source
In this study, we analyze functional data of the same 14 participants being part
of the studyforrest dataset
(\href{http://www.studyforrest.org}{studyforrest.org};
\citep{hanke2014audiomovie, hanke2016simultaneous}).
% PPA + movie + audio-description
We annotated cuts in the movie ``Forrest Gump'' \citep{ForrestGumpMovie}, and
words spoken by an additional narrator in the movie's audio-description (i.e.
the movie's audio-only variant; \citep{ForrestGumpGermanAD}) to exploratorily
investigate how the parahippocampal gyrus behaves during movie watching and
listening to an ``audiobook''.
% focus on audio-description
Encouraged by \citep{aziz2008modulation}, we also employ a traditional GLM, and
focus on the audio-description as a naturalistic, auditory-only paradigm free
from any task to localize a ``visual area'' in individual study participants.
% comparison to dedicated localizer
We also compare our results to results of a dedicated visual localizer
experiment done with the same participants \citep{sengupta2016extension}.

@@

% intro
We used data from three publicly available datasets
(\href{http://www.studyforrest.org}{studyforrest.org}) which have already been
used by other research groups for independent research questions.
% used studies
\todo{this is just loveless listing so far but it's 'complete'} The same
subjects were
% AO
a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding,
nguyen2016integration},
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}), a dataset already used by
\citep{ben2018hippocampal},
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study; \citep{sengupta2016extension}), a dataset already used by
\citep{jiahui2019predicting}.
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications. Following is a summary of most important aspects.

@@

\subsection{Stimuli}
% AO & AV stimulus name & references
We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie
``Forrest Gump'' \citep{ForrestGumpMovie} and its temporally aligned
audio-description that was broadcast as an additional audio track for visually
impaired listeners on Swiss public television \citep{ForrestGumpGermanAD}.
% AV: voice-over
The plot of the movie is already carried by an voice-over of the main character
Forrest Gump.
% AO: additional narrator
In the largely identical audio-description, an additional male narrator
describes essential aspects of the visual scenery when there is no off-screen
voice, dialog, or other relevant auditory content.

@@

% VIS study picture categories
All stimuli for the VIS study were already used in a previous study
\citep{haxby2011common}. There were 24 unique grayscale images (matched in
luminance, size of 400 $\times$\unit[400]{px}) for each of six stimulus
categories: human faces, human bodies without heads, small objects, houses and
outdoor scenes comprising of nature and street scenes, and phase scrambled
images. Mirrored views of these 24 $\times$ 6 images were also used as stimuli.

@@

groom & elements defining a locale's spatial layout & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII \tabularnewline

@@

% intro
For the AO stimulus, we created eight $t$-contrasts presumably correlating with
increased hemodynamic activity in the PPA by contrasting different kind of
descriptive nouns.
% furniture: blurred border between groom and object
We did not use the category ``furniture'' (\texttt{furn}) as a regressor in one
of the contrasts of interest because this category was considered to eighter
count as object or a geometry-defining structure of a room/locale.
% negative control contrasts
Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created for negative
control purposes to test if increased activation in the PPA was correlated with
moments of cuts and therefore correlated with a possibly accompanying change in
the soundscape (anticipating the narrator's cue of a switch to new setting, too).

@@

\subsection{individual results}
% why individual results in the first place.
We also investigated localization performance of both naturalistic paradigms on
the level of individual subjects. \todo{maybe report the other reason here, too:
which subjects influence the group results the most? ``multiple localizer''?}
% results in both subject and group space
Time series of all subjects were analyzed both in subject space and group space.
% individual z-maps
Results of the analyses that were performed in each subject's subject-space
(unthresholded $z$-maps and thresholded $z$-maps with Z>2.3, p<.05) can be
found in the accompanying dataset.
% why
For better comparison of results across participants, we show results ($z$-maps;
Z>3.4, p<.05 cluster-corrected) of the analyses that was performed in group
space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AO
and AV $t$-contrast, and the outline of the individual PPAs
\citep{sengupta2016extension} overlayed on the MNI152 template (horizontal slice
z=-11 for all subjects).
% results in detail voxels of significant clusters in PPA ROI (and  RSC
% liberally)
% sub-01: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
% sub-02: PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
% sub-03: PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
% sub-04: PPA (-/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-) !
% sub-05: PPA (l/r), AO (-/-), AV (-/-); RSC: AO (-/-), AV (-/-)
% sub-06: PPA (l/r), AO (l/r), AV (-/-); RSC: AO (l/-), AV (-/-)
% sub-09: PPA (l/r), AO (l/-), AV (l/r); RSC: AO (l/r), AV (l/r)
% sub-14: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
% sub-15: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
% sub-16: PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/-)
% sub-17: PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/r)
% sub-18: PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (-/r)
% sub-19: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
% sub-20: PPA (-/r), AO (-/-), AV (l/r); RSC: AO (-/-), AV (-/-)

% PPA ROI (Sengupta et al., 2016)
The dedicated localizer shows bilateral clusters in 12 subjects and unilateral
right clusters in two subjects (sub-04, sub-20).
% subjective threshold
Noteworthy, ROIs were assessed by \citep{sengupta2016extension} by visually
inspecting the unthresholded $z$-maps, and setting a subjectively best fitting
$z$-threshold to isolate a cluster in the PPA.
% AO
In the current analysis of the AO stimulus, we find significant bilateral
clusters in nine subjects, and one significant cluster in the left hemisphere of sub-09.
% subj-04
In sub-04, two homologous clusters are apparent, where the dedicated localizer
yielded only one cluster in the right hemisphere.
% AV
For the AV stimulus, results show homologous clusters in five subjects, and
unilateral right clusters in seven subjects (of which one subjects also yielded
just a unilateral cluster in the dedicated localizer).
% difference to dedicated localizer
In sub-20 bilateral, where the dedicated localizer yielded only one cluster in
the right hemisphere.

@@

\todo[inline]{tailor it to points mentioned in the introduction (full circle);
print intro to avoid constant scrolling}

\subsection{intro}
\todo[inline]{summary of study goal and methods}
% what we did
We used two naturalistic stimuli and their annotations to create a GLM
presumably correlating with hemodynamic activity in the PPA. We focused on the
AO stimulus but also build contrasts for the AV stimulus for cross-modal
control.

\subsubsection{correlation of regressors} Both stimuli were not designed to
maximize detection power in an fMRI experiment bu to entertain the audience.
% why we created the correlation matrix in the first place
We tested for correlation of stimulus features because a high degree of shared
variance prevents detection power.
% summary of results
Results show only minor to no correlations of regressors across all stimulus
segments
% statement
Hence depending on the stimulus features of interest, it is feasible to use
specific stimulus features of a regular movie or audiobook for neuroscientific
research questions.

@@

\subsubsection{AO stimulus}
% AO stimulus cluster location
The results of the AO stimulus yielded isolated clusters in the anterior part of
the PPA ROI (overlap of individual PPAs taken from Sengupta et al.).
% comparison to other studies using ISC
\todo[inline]{check Wilson (2008), Lerner (2011), Honey (2012), Silbert (2014).
Do they find ISC in PPA using an auditory stimulus? As far as I remember they
don't}
% diff to Aziz (2008)
Unlike \citep{aziz2008modulation} we did not use whole sentences as events to
model a hemodynamic response but the length of the word giving the cue about the
visual content of a scene.
% no task
Compared to previous studies (O'Craven \& Kanwisher: mental imagery
hypothesis)\todo{check this paper out} participants of our study were not
instructed to form a vivid mental image of the stimulus but to ``enjoy the
audiobook''.
% naive to the research question
Moreover, participants could not infer the perceptual process to be investigated
by merely being submitted to the stimuli / experimental design.
% concluding statement
This suggest the PPA is involved in processing incidental spatial information
embedded in a rich auditory stream, and this involvement does not rely on
creating a mental imagery or deliberately paying close attention to spatial
features.\todo{kinda similar to Wolbers (2011) who checked connectivity between
    PPA and visual cortex during haptic exploration of LEGO scenes}

% other
\todo[inline]{Aminoff (2013). PPA's role in cognition regarding non-spatial
    stuff: ``Although the PHC is commonly thought of as responding to visual
    stimuli, it has also been found to elicit activity for auditory stimuli
    [25,26,30,31] and to respond to odor stimuli [32–34]''.}
% concluding statement
In summary, our group results suggest that auditory spatial information does not
just modulate activity in the PPA (depending on other factory like familiarity,
XY; s. Aziz) but correlates with bilaterally increased
activation.\todo{``modulate'' suggests causation}

>>>>

@@

% brain mapping via fMRI
Cognitive neuroscientists use brain imaging methods like blood oxygenation
level-dependent functional magnetic resonance imaging (BOLD fMRI) to map
perceptual and cognitive brain processes (e.g. viewing of landscapes,
\citep{epstein1998ppa}; or theory of mind \citep{spunt2014validating}) to
functional brain areas or networks.
% What is the PPA?
A classic example of a functionally defined, higher-level visual area is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacant
regions of the fusiform gyrus \cite{epstein1998ppa} at the boundary to the anterior lingual gyrus \citep{epstein2008parahippocampal}.
% neural correlate of scene perception
Increased hemodynamic activity in the PPA correlates with the perception of
static pictures of landscapes or landmarks compared to pictures of tools or
faces.
% spatial layout hypothesis
According to the spatial layout hypothesis, the PPA is involved in processing
the surface geometry of a visual stimulus and possibly in identifying scenes
based on their spatial layout \citep{epstein2010reliable}.
% literature review overview 1: imagination & haptic exploration
At a group average level, results generalize to mental imagination of landscapes
\citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO
blocks \citep{wolbers2011modality}.
% literature review overview 2: spoken sentences
One study that used spoken, place-related sentences showed significantly
decreased activation in the left and no modulation in the right-hemispheric PPA
\citep{aziz2008modulation}.

@@

% Wolbers: haptic exploration
In the block design study conducted by \citep{wolbers2011modality} the PPA of
sighted participants showed increased activation during a delayed
matching-to-sample task of haptically explored scenes constructed from LEGO
bricks compared to haptically explored abstract geometric objects.
% connectivity analysis by Wolbers
\todo[inline]{Er hat noch eine Connectivitäts-Analyse mit dem Occipital Cortex
    gemacht. Im Vergleich zum visuellen Paradigma ist im haptischen Paradigma
    keine Connectivität. Interpretation: Es kann keine mental imagery sein;
    ``The scene-related increase in coupling with the PPA was significantly
stronger in multiple clusters in occipital cortex under visual than haptic
stimulation (Figure 2B; Table S2)''}
% Aziz (2008): place related sentences
\todo[inline]{lass uns kurz im Gespräch über Aziz Paper gucken; die relvanten
    Abschnitte sind in der PDF markiert. Ihre Method Section ist ``strange'' und
    im Grunde kommt überall nur uneinheitliche Grütze heraus; ich blicke nicht
    durch, weshalb folgendes nicht vollständig korrekt sein wird;so wie ich es
verstanden habe, hat sie den Unterschied zwischen PPA und FFA angeguckt, aber
diesen Unterschied im Kontrast zu object-related Sentences (dortige Fig 3)}
% Aziz' stimuli
To our knowledge only one study \citep{aziz2008modulation} correlated
hemodynamic activity of the PPA with spoken sentences. Sentences described
generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting
pool''), faces  (``Marilyn Monroe has a large square jaw''), or objects (``The
television has a long antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.

@@

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% shortcomings of previous studies: simplified stimuli
Nevertheless, all reviewed studies have in common that they employed a small set
of simplified stimuli to strictly control experimental conditions.
% shortcomings of previous studies: task-based paradigm
Further, they usually relied on explicit judgment-based tasks to ensure that
participants payed attention to the stimuli.
% disadvantage 1b: lack of validity
Paradigms using block designs accompanied with a task have the disadvantage that
they do not resemble our real-life experience and thus lack external validity
\citep{westfall2016fixing} as well as ecological validity
\citep{hasson2004intersubject}.
% disadvantage 2a: averaging for group results
Additionally, the reviewed studies averaged results across 7-11 subjects to
improve the signal-to-noise-ratio (SNR).
% disadvatage 2b: no individual level
The disadvantage here is that the averaging approach does not characterize brain
functions at an individual level, a prerequisite for the application of brain
imaging methods in individual diagnostics (cf. \citep{dubois2016building,
eickhoff2020towards}).
% open questions
This raises the question how the PPA behaves under life-like conditions, and how
group results a driven by individuals subjects especially in response to
audio-only stimulation\todo{``audio-only'' sounds meh}.
% Huth (2016)
\todo[inline]{but Huth et al. (2016) implicitly regarding audio-only; but they
do not discuss the PPA; moreover, they do voxel-wise encoding which doesn't say
anything about excitation/inhibition}

% naturalistic stimuli
Paradigms using naturalistic stimuli like movies
\citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{honey2012not, lerner2011topographic, silbert2014coupled} offer complex,
continuous stimulation that better resemble our experience of a our dynamic
environment.
% naturalistic stimuli review: intro
Two early studies using naturalistic stimuli suggest functional specialization
of brain areas is preserved during movie watching when many perceptual and
cognitive processes are triggered simultaneously \citep{bartels2004mapping,
hasson2004intersubject}.
% Bartels (2004): Film + GLM (but surprisingly did not annotate landscapes)
\citep{bartels2004mapping} manually annotated time points that depict faces and
human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}
\citep{tomorrowneverdies}.
% Bartels: results
Employing a general linear model (GLM) to model hemodynamic activity, these time
points correlated with increased activity in the ``fusiform face area''
\citep{kanwisher1997ffa} and ``extrastriate body area''
\citep{downing2001bodyarea} respectively.
% Hasson (2004): Film + (reverse) ISC
Employing a reverse intersubject correlation, \citep{hasson2004intersubject}
used a 30 minute clip of the movie \textit{The Good, the Bad, and the Ugly}
\citep{goodbadugly}.
% Hasson: method
fMRI brain volumes showing the highest hemodynamic activity in the PPA [across
(five) participants] were matched to the temporally corresponding movie frames.
% Hasson: results
Results revealed that corresponding movie frames depicted indoor and outdoor
scenes including buildings and open fields.
% summary naturalistic stimuli
Nevertheless, both studies used an audio-visual stimulus and again do not
address the question how the investigated functional areas respond an audio-only
stimulus.

\todo[inline]{mih: Possibly cite DuPre (2019) and declare that this study is a
    concrete realization; COH: I read it but don't know what/how to cite it for
    any other reason than just to cite it (here or in discussion)}

% what we did: data source
In the current study, we analyze publicly available functional data
(studyforrest.org) of the same 14 participants watching a movie
\citep{hanke2016simultaneous} and listening to an audiobook.
\citep{hanke2014audiomovie}.
% PPA + movie + audio-description
We annotated cuts in the movie ``Forrest Gump'' \citep{ForrestGumpMovie}, and
words spoken by an additional narrator in the movie's audio-description (i.e.
the movie's audio-only variant; \citep{ForrestGumpGermanAD}) to exploratorily
investigate how the parahippocampal gyrus behaves during more life-like
conditions free from any task.
% focus on audio-description
Encouraged by \citep{aziz2008modulation}, we focus on the audio-description as
an audio-only paradigm and test its localization performance of a ``visual
area'' in individual study participants.
% comparison to dedicated localizer
Finally, we compare these results to results of a dedicated visual localizer
experiment done with the same participants \citep{sengupta2016extension}.

@@

% intro
We used data from three publicly available datasets
(\href{http://www.studyforrest.org}{studyforrest.org}) that have already been
used by other research groups for independent research questions.
% used studies
\todo{this is just loveless listing so far} The same subjects were
% AO
a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding,
nguyen2016integration},
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}), a dataset already used by
\citep{ben2018hippocampal},
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study; \citep{sengupta2016extension}), a dataset already used by
\citep{jiahui2019predicting}.
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications. Following is a summary of most important aspects.

@@

\subsection{Stimuli}
% AO & AV stimulus name & references
We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie
``Forrest Gump'' \citep{ForrestGumpMovie} and its temporally aligned
audio-description that was broadcast as an additional audio track for visually
impaired listeners on Swiss public television \citep{ForrestGumpGermanAD}.
% AV: voice-over
The plot of the movie is already carried by a voice-over of the main character
Forrest Gump.
% AO: additional narrator
In the largely identical audio-description, an additional male narrator
describes essential aspects of the visual scenery when there is no off-screen
voice, dialog, or other relevant auditory content.

@@

% VIS study picture categories
All stimuli of the VIS study were already used in a previous study
\citep{haxby2011common}. There were 24 unique grayscale images (matched in
luminance, size of 400 $\times$\unit[400]{px}) for each of six stimulus
categories: faces, bodies without heads, small objects, houses and
outdoor scenes comprising of nature and street scenes, and phase scrambled
images. Mirrored views of these 24 $\times$ 6 images were also used as stimuli.

@@

groom & elements defining geometry of local space & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII \tabularnewline

@@

% intro
For the AO stimulus, we created eight $t$-contrasts presumably correlating with
increased hemodynamic activity in the PPA by contrasting different kind of
descriptive nouns.
% furniture: blurred border between groom and object
We did not use the category ``furniture'' (\texttt{furn}) as a regressor in one
of the contrasts of interest because this category was considered to eighter
count as object or a geometry-defining structure of a room/locale.
\todo[inline]{Epstein (2008): response to arrays of objects drawn from the rooms
    but displayed on a blank background is quite weak [11]}
% negative control contrasts
Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created for negative
control purposes to test if increased activation in the PPA was correlated with
moments of cuts and therefore correlated with a possibly accompanying change in
the soundscape (anticipating the narrator's cue of a switch to new setting,
too).

@@

\subsection{individual results}
% why individual results in the first place.
We also investigated localization performance of both naturalistic paradigms on
the level of individual subjects. \todo{maybe report the other reason here, too:
which subjects influence the group results the most? ``multiple localizer''?}
% results in both subject and group space
Time series of all subjects were analyzed both in subject space and group space.
% individual z-maps
Results of the analyses that were performed in each subject's subject-space
(unthresholded $z$-maps and thresholded $z$-maps with Z>2.3, p<.05) can be
found in the accompanying dataset.
% why
For better comparison of results across participants, we show results ($z$-maps;
Z>3.4, p<.05 cluster-corrected) of the analyses that was performed in group
space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AO
and AV $t$-contrast, and the outline of the individual PPAs
\citep{sengupta2016extension} overlayed on the MNI152 template (horizontal slice
z=-11 for all subjects).
% results in detail voxels of significant clusters in PPA ROI (and  RSC
% liberally)
% sub-01 (m): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
% sub-02 (m): PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
% sub-03 (f): PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
% sub-04 (f): PPA (-/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-) !
% sub-05 (m): PPA (l/r), AO (-/-), AV (-/-); RSC: AO (-/-), AV (-/-)
% sub-06 (m): PPA (l/r), AO (l/r), AV (-/-); RSC: AO (l/-), AV (-/-)
% sub-09 (m): PPA (l/r), AO (l/-), AV (l/r); RSC: AO (l/r), AV (l/r)
% sub-14 (f): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
% sub-15 (m): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
% sub-16 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/-)
% sub-17 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/r)
% sub-18 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (-/r)
% sub-19 (f): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
% sub-20 (f): PPA (-/r), AO (-/-), AV (l/r); RSC: AO (-/-), AV (-/-)

% PPA ROI (Sengupta et al., 2016)
The dedicated localizer shows bilateral clusters in 12 subjects and unilateral
right clusters in two subjects (sub-04, sub-20).
% subjective threshold
Individual ROIs were assessed by \citep{sengupta2016extension} by visually
inspecting unthresholded $z$-maps, and setting a subjectively best fitting
$z$-threshold to isolate a cluster in the PPA.
% AO
In the current analysis of the AO stimulus, we find significant bilateral
clusters in nine subjects, and one significant cluster in the left hemisphere of
sub-09.
% subj-04
In sub-04, two homologous clusters are apparent, where the dedicated localizer
yielded only one cluster in the right hemisphere.
% AV
For the AV stimulus, results show homologous clusters in five subjects, and
unilateral right clusters in seven subjects (of which one subjects also yielded
just a unilateral cluster in the dedicated localizer).
% difference to dedicated localizer
In sub-20 bilateral, where the dedicated localizer yielded only one cluster in
the right hemisphere.

@@

\subsection{intro}
\todo[inline]{goal and what we did should probably in result section}
% study goal
The goal of this study was to investigate if increased hemodynamic activity in
the PPA correlates with spatial information presented under more ecological
valid conditions.\todo{cautious phrasing but still problematic: looking for
confirmation}
% what we did
We used annotations of a \unit[2]{h} movie and it's temporally aligned
audio-description to create GLMs of hemodynamic activity resembling analyses
of previous studies using simplified stimuli.

\todo[inline]{summary of results like ``Our results demonstrate that\dots''}

\subsubsection{correlation of regressors}
% stimuli not designed for research purposes
Both stimuli were not designed to for research purposes detection power in a
fMRI experiment) but to entertain their audiences.
% why we created the correlation matrix in the first place
We first tested for correlation of stimulus features because a high degree of
shared variance lowers detection power.
% summary of results
Results show only minor to no correlations of regressors across all stimulus
segments.
% statement
Hence depending on the stimulus features of interest, it was feasible to use the
annotated stimulus features for our research question.

@@

\subsubsection{AO stimulus}
% AO stimulus cluster location
The results of the AO stimulus yielded isolated clusters in the anterior part of
the PPA ROI (overlap of individual PPAs taken from Sengupta et al.).
% comparison to other studies using ISC
\todo[inline]{check Wilson (2008), Lerner (2011), Honey (2012), Silbert (2014).
Do they find ISC in PPA using an auditory stimulus? As far as I remember they
don't}
% diff to Aziz (2008)
Unlike \citep{aziz2008modulation} we did not use whole sentences as events to
model a hemodynamic response but the length of the word giving the cue about the
visual content of a scene.
% no task
Compared to \citep{ocraven2000mental} participants of our study were not
instructed to form a vivid mental image of the stimulus but to ``enjoy the
audiobook''. This procedure resembles experiencing the world around us in
real-life more closely
% naive to the research question
Moreover, participants could not infer the perceptual process to be investigated
by merely being exposed to the stimuli / experimental design. This suggests
spatial information is processed in the PPA despite a lack of visual
attention.\todo{bold claim here}
% comparison to Wolbers
Similarly to \citep{wolbers2011modality} who found increased activation in the
PPA when blind study participants haptically explored scenes made out of LEGO
blocks compared to other objects, our results support the hypthesis that
increased activation in the PPA does not necessarily rely on creating a vivid
mental image.
% (visual or auditory) spatial attention
Results further suggest activation does also not rely on deliberately paying
auditory attention to spatial information embedded in a complex/rich auditory
stimulus.\todo{kinda bold statement}
% others
\todo[inline]{Aminoff (2013). PPA's role in cognition regarding non-spatial
stuff: ``Although the PHC is commonly thought of as responding to visual
stimuli, it has also been found to elicit activity for auditory stimuli
[25,26,30,31] and to respond to odor stimuli [32–34]''.}
% concluding statement
In summary, our group results suggest that auditory spatial information does not
just modulate activity in the PPA (depending on other factory like familiarity,
XY; s. Aziz) but correlates with bilaterally increased
activation.\todo{``modulate'' suggests causation}
